### 2014-03-14 src/analysis.Rnw
Alex changes

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criteria, we computed the
correlation between sampled mutation score and full mutation score.
Since for most of the sampling criteria, if there are no mutants to
sample, it probably means there are no mutants generated on the whole,
we used
\[\mu_\{M_{all}|M_{reduced}\} = 0 + \beta_1 \times M_{reduced}\]
as the regression formula, and report
the correlation from this linear regression. We also report the expected
multiplier factor $\beta_1$ for the sampled mutation score. This factor
determines the ease of satisfying the sampling criteria. That is, if the
multiplier factor is small, then it is easier to satisfy compared to a
larger multiplier factor.

Next, for each criteria, we computed the reduction of mutants given by the
ratio between total number of mutants and sampled mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. (A large amount of standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. So as a heuristic, we suggest looking at only those projects which
has a mean reduction ratio at least twice the standard deviation.)

A few projects did not return any results for some large reduction factors.
This number of valid results from projects are also collected in the result
tables.

>>>>

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criteria, we computed the
correlation between sampled mutation score and full mutation score.
Since for most of the sampling criteria, if there are no mutants to
sample, it probably means there are no mutants generated on the whole,
we used
\[\mu_\{M_{all}|M_{reduced}\} = 0 + \beta_1 \times M_{reduced}\]
as the regression formula, and reported
the correlation for this linear regression. We also report the expected
multiplier factor $\beta_1$ for the sampled mutation score. This factor
determines the ease of satisfying the sampling criteria. That is, if the
multiplier factor is small, then it is easier to satisfy compared to a
larger multiplier factor.

Next, for each criteria, we computed the reduction of mutants given by the
ratio between total number of mutants and sampled mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. A large amount of standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. So as a heuristic, we suggest looking at only those methods which
have a mean reduction ratio at least twice the standard deviation.

A few projects did not return any results for some large reduction factors.
Thus number of valid results from projects is also collected in the result
tables.

### 2014-03-14 src/conclusion.Rnw
udpate
Alex changes

Our analysis suggests that simple random sampling, that is, at the project level works best when compared to more sophesticated schemes of sampling. Further, we also note that random sampling performs better in predicting final mutation score when compared against operator selection.

This suggests that the best way to reduce the computational requirements while trying to build a representative set is to randomly sample on the whole set of mutants directly.

>>>>

Our analysis suggests that simple random sampling --- that is, at the
project level --- works best when compared to more sophesticated schemes of
sampling. Further, we also note that random sampling performs better in
predicting final mutation score than operator selection.

This suggests that the best way to reduce the computational
requirements of mutation analysis is fortunately easy to apply in
almost any setting, given a tool that produces a good starting set of
mutants.  Namely, randomly sampling the total mutant population, even
with very small sample sizes, can effectively predict the results of
running all mutants, but at only a fraction of the computational cost.
Not only is this method simple and effective, but it is also quite
stable comapred to some alternatives, with a low standard deviation in
effectiveness across projects, for both original and random test suites.

There is a second possible point of interest here: as with coverage
metrics used to predict mutation scores~\cite{gopinath2014code}, using
a large body of actual open source code to perform experiments seems
to favor simple and easily-implemented approaches much more strongly
than limited experiments on more academic subjects.  We speculate that
the inadequacies in real world test suites, or even in randomly
generated tests for real world programs, may frequently be more simply
predicted and evaluated than for typical research subjects, which may
be smaller or involve less easily distinguished test suites.

### 2014-03-14 src/discussion.Rnw
Alex changes

The second pattern is that fractional sampling based on projects appears to be
better than that based on classes, which in turn is better than methods and
lines, with regard to the stability of the result (i.e low sd).
This seems not very visible at lower levels (where the reduction fraction is less
than 32), but becomes more pronounced as the mutant reduction fraction increases.
There seem to exist a hierarchy of sampling, where by as you go more fine grained,
the stability decreases.
We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where by
the method based sampling had the highest accuracy. In fact, in our measurements,
the opposite may be true, with project based sampling getting the highest correlation
with the final score a majority of the time.

>>>>

The second pattern is that fractional sampling based on projects appears to be
better than that based on classes, which in turn is better than methods and
lines, with regard to the stability of the result (i.e. low standard deviation).
This seems not very visible at lower levels (where the reduction fraction is less
than 32), but becomes more pronounced as the mutant reduction fraction increases.
There seem to exist a hierarchy of sampling, where by as sampling becomes more fine grained stability decreases.
We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where method-based sampling had the highest accuracy. In fact, in our measurements,
the opposite may be true, with project based sampling getting the highest correlation
with the final score a majority of the time.

### 2014-03-14 src/results.Rnw
Alex changes

Our results for random sampling over program elements using $sample(x)$
are given in Table~\ref{tbl:xselsample}. The result of its variation, using
$round(x)$ is given in Table~\ref{tbl:xselround}, and that using
$ceil(x)$ is given in Table~\ref{tbl:xselceil}.
The first column in each table provides the scope of sampling i.e. if it was
done per class, per method, per line etc. The second column provides the
fraction involved.  Third column contains the $R^2$ value obtained between
the mutation score of the sampling criteria used and the full mutation score.
The fourth column contains the mutant reduction factor. This is the average of
total mutants produced divided by the number of mutants sampled by the criteria.
Fifth column contains the standard deviation of the same. A few of the projects
did not return any value for certain sampling criteria for particular mutation
reduction fractions. The sixth column contains the number of projects that
actually had valid values for the criteria being considered. The seventh column
is the average multiplier between the sampled mutation score and the full mutation
score.

The Table~\ref{tbl:lcountl} provides the results for line count criteria where the
sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
the results for line count criteria where the sampling was conducted inside the
program element. Similarly the Table~\ref{tbl:onesel} contains the results for
the criteria of one mutant per program element.

The same (only for original test suite) is visualized in Figure~\ref{fig:xroundsel}.

>>>>

Our results for random sampling over program elements using $sample(x)$
are given in Table~\ref{tbl:xselsample}. The result of the variation using
$round(x)$ is given in Table~\ref{tbl:xselround} and that using
$ceil(x)$ is given in Table~\ref{tbl:xselceil}.
The first column in each table provides the scope of sampling i.e. if it was
done per class, per method, per line etc. The second column provides the
fraction involved.  The third column contains the $R^2$ value obtained between
the mutation score of the sampling criteria used and the full mutation score.
The fourth column contains the mutant reduction factor. This is the average of
total mutants produced divided by the number of mutants sampled by the criteria.
The fifth column contains the standard deviation of the same. A few of the projects
did not return any value for certain sampling criteria for particular mutation
reduction fractions. The sixth column contains the number of projects that
actually had valid values for the criteria being considered. The seventh column
is the average multiplier between the sampled mutation score and the full mutation
score.

Table~\ref{tbl:lcountl} provides the results for line count criteria where the
sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
the results for line count criteria where the sampling was conducted inside the
program element. Similarly Table~\ref{tbl:onesel} contains the results for
the criteria of one mutant per program element.

The same data (only for original test suite) is visualized in Figure~\ref{fig:xroundsel}.

### 2014-03-14 src/threats.Rnw
Alex changes

\section{Threats to Validity}
While we have taken every care to ensure that our results are valid, and to eliminate the
effects pf random noice in experiments, our results are subject to the following threats
to validity.

Our results were observed on open source Java programs from Github repository, using the
maven build system. Further, only those projects that successfully completed mutation
testing within a designated amount of time were chosen. This implies that if there is a
confounding factor in play that affects the relation between the full mutation score and
sampling mutation score, and any of the noted factors, it might cause our results to be
either wrong or less applicable.

Secondly, we had to rely on the PIT mutation testing tool, and had to extend its capabilities
to some extent for our purposes. Software bugs are a fact of life. While every care has been
taken to avoid them, there is still some probability of some bugs having escaped us.

>>>>

\section{Threats to Validity}
While we have taken every care to ensure that our results are valid, and to eliminate the
effects of random noise in experiments, our results are subject to the following threats
to validity.

Our results were observed on open source Java programs from the Github repository, using the
maven build system. Further, only those projects that successfully completed mutation
testing within a designated amount of time were chosen. This implies that if there is a
confounding factor in play that affects the relation between the full mutation score and
sampling mutation score, and any of the noted factors, it might cause our results to be
either wrong or less applicable.

Secondly, we had to rely on the PIT mutation testing tool, and had to extend its capabilities
to some extent for our purposes. Software bugs are a fact of life. While every care has been
taken to avoid them, there is still some possibility of some bugs having escaped us.
